### 2022-02-23 paper/Chapters/Background.tex
Feedback from advisor

Computers have a long history of being built to serve a particular purpose, often compromising some aspects of the system to bolster others.
Chapter \ref{SpecializationOfComputers} discusses the history of how computers were built for a particular function, and how the advancement of technology has brought the \enquote{Personal Computer} seen know today.
Chapter \ref{PowerOfTheDesktop} discusses the benefits of a desktop computer, Chapter \ref{ConvenienceOfTheLaptop} discusses the benefits and drawbacks of a laptop computer, and Chapter \ref{RiseOfTheGamingLaptop} discusses the rise of the gaming laptop and the closing gap between power and portability at the cost of increased price.
Chapter \ref{ThinClients} briefly discusses thin clients, a corporate solution for remote access to a computer.
Chapter \ref{ApplicationToModernDay} introduces current world wide context that has an impact on the computing world and the need for power and portability.

>>>>

Computers have a long history of being built to serve a particular purpose, often compromising some aspects of the system to bolster others.
Chapter \ref{sec:SpecializationOfComputers} discusses the history of how computers were built for a particular function, and how the advancement of technology has brought the \enquote{Personal Computer} seen know today.
Chapter \ref{subsec:PowerOfTheDesktop} discusses the benefits of a desktop computer, Chapter \ref{subsec:ConvenienceOfTheLaptop} discusses the benefits and drawbacks of a laptop computer, and Chapter \ref{subsec:RiseOfTheGamingLaptop} discusses the rise of the gaming laptop and the closing gap between power and portability at the cost of increased price.
Chapter \ref{sec:ThinClients} briefly discusses thin clients, a corporate solution for remote access to a computer.
Chapter \ref{sec:ApplicationToModernDay} introduces current world wide context that has an impact on the computing world and the need for power and portability.

### 2022-02-23 paper/Chapters/StateOfTheArt.tex
Feedback from advisor

While there are many applications in existence that allow a user to remotely control a computer from another location, few of them offer the power required to stream high-performing applications to a remote device.
The following subsections will introduce existing attempts to solve this problem as well as drawbacks that come with each implementation.

@@

Although it is the built-in solution for Windows machines, it isn't without it's drawbacks.
Firstly, only one graphical session is active at one time while using windows.
This means if a user is logged into the host computer and someone initiates a connection with RDP, the user using the host computer will be logged out.
While this isn't always an issue, sensitive programs that don't take well to being logged out may run into issues.
Secondly, RDP does not support relative mouse movement \cite{burgin_2013}.
This means every mouse input is sent to the host computer as an absolute position on the screen, rather than as a relative distance from it's previous location.
Again, while this isn't always an issue, any application that moves the mouse for the user, such as controlling 3D applications or anything dealing with virtual cameras such as animation or game development, cannot be controlled properly.

@@

As discussed in Section \ref{sec:ThinClients}, Thin Clients are a device commonly seen in the corporate world to allow employees to access data centers and computing clusters from their desks.
Due to their low cost and ease of deployment, they are often the device of choice to enable employees to access the full power of the business' computing infrastructure without needed to purchase a powerful device for each employee.
However, since a typical thin client is a headless device, meaning it doesn't come with a monitor, keyboard, mouse, or other peripherals, they are often less portable as one might thing.
A thin client is usually set up once, and then left in that place for as long as a desktop would stay.
Especially with laptop sales on the rise, thin clients do not have the benefit of being more portable than the alternatives.

@@

The Nvidia Shield game console was Nvidia's first foray into the realm of remote streaming.
Though it was focused on gaming and media streaming, it was one of the first attempts at using a portable device to stream intensive applications such as games from a host computer \cite{brown_2013}.
At the steep price point of \$349, it definitely was enthusiast hardware for a device that focused on mobile and desktop gaming over running console games or demanding titles locally.
But while the the physical device was praised for performance, battery life, and the experience of streaming games to the console, it didn't perform too well in terms of sales.
It was still widely regarded as a technological breakthrough though, and Nvidia continued to develop the technology into a new device called the Nvidia Shield TV \cite{daniel_2017}.
Focused on bringing the power of a gaming desktop to a TV, the Nvidia Shield TV dropped the idea of portability in favor of filling a different market focused on comfort.
While this is no longer a valid device for the purposes of this paper, the developments of the proprietary GameStream technology that powered the Shield and the Shield TV proved to be even more exciting than the physical devices themselves.
\todo{Does the picture look ok?}

>>>>

While there are many applications in existence that allow a user to remotely control a computer from another location, few of them offer the \todo{Clarify power, since the issue isn't processing power}power required to stream high-performing applications to a remote device.
The following subsections will introduce existing solutions to this problem as well as drawbacks that come with each implementation.

@@

Although it is the built-in solution for Windows machines, it isn't without it's drawbacks.
Firstly, only one graphical session is active at one time while using windows.
This means if a user is logged into the host computer and someone initiates a connection with RDP, the user using the host computer will be logged out.
While this isn't always an issue, sensitive programs that don't take well to being logged out may run into issues.
Secondly, RDP does not support relative mouse movement \cite{burgin_2013}.
\todo{explain further}
This means every mouse input is sent to the host computer as an absolute position on the screen, rather than as a relative distance from it's previous location.
Again, while this isn't always an issue, any application that moves the mouse for the user, such as controlling 3D applications or anything dealing with virtual cameras such as animation or game development, cannot be controlled properly.

@@

As discussed in Section \ref{sec:ThinClients}, Thin Clients are a family of devices commonly seen in the corporate world to allow employees to access data centers and computing clusters from their desks.
Due to their low cost and ease of deployment, they are often the device of choice to enable employees to access the full power of the business' computing infrastructure without needed to purchase a powerful device for each employee.
However, since a typical thin client is a headless device, meaning it doesn't come with a monitor, keyboard, mouse, or other peripherals, they are often less portable as one might think.
A thin client is usually set up once, and then left in that place for as long as a desktop would stay.
Especially with laptop sales on the rise, thin clients do not have the benefit of being more portable than the alternatives.

@@

The Nvidia Shield game console was Nvidia's first foray into the realm of remote streaming.
Though it was focused on gaming and media streaming, it was one of the first attempts at using a portable device to stream intensive applications such as games from a host computer \cite{brown_2013}.
At the steep price point of \$349, it definitely was enthusiast hardware for a device that focused on mobile and desktop gaming over running console games or demanding titles locally.
But while the the physical device was praised for performance, battery life, and the experience of streaming games to the console, it didn't perform too well in terms of sales.
It was still widely regarded as a technological breakthrough though, and Nvidia continued to develop the technology into a new device called the Nvidia Shield TV \cite{daniel_2017}.
Focused on bringing the power of a gaming desktop to a TV, the Nvidia Shield TV dropped the idea of portability in favor of filling a different market focused on comfort.
While this is no longer a valid device for the purposes of this paper, the developments of the proprietary GameStream technology that powered the Shield and the Shield TV proved to be even more exciting than the physical devices themselves.
